### 2014-04-24 HowtoHowtoCapon/submission/submit1/answer/answer.tex

\qi{On page 6, authors say "The bottleneck in the final design is now the inversion step, which is typically 5 times slower than the build step". Surely, this merits an explanation. What is the final design being compared with? What was the expectation? What changed? Figure 3 shows FLOPs before optimization - this shows build and inversion steps of roughly the same order of magnitude in the right half of the figure. Does Figure 3 set the expectation? Figure 5 shows "relative complexity reduction" of entire pro-cess, so there is no information on relative speed of build and inversion steps. Figure 10 shows estimated FLOPs for the two steps, but since both steps have different theoretical complexities (operations counts), and the two steps do not optimize the same way, this does not provide an expectation of the relative times.}
\ai{TODO}

>>>>

\qi{On page 6, authors say "The bottleneck in the final design is now the inversion step, which is typically 5 times slower than the build step". Surely, this merits an explanation. What is the final design being compared with? What was the expectation? What changed? Figure 3 shows FLOPs before optimization - this shows build and inversion steps of roughly the same order of magnitude in the right half of the figure. Does Figure 3 set the expectation? Figure 5 shows "relative complexity reduction" of entire process, so there is no information on relative speed of build and inversion steps. Figure 10 shows estimated FLOPs for the two steps, but since both steps have different theoretical complexities (operations counts), and the two steps do not optimize the same way, this does not provide an expectation of the relative times.}
\ai{The explanation is provided in the section V, the discussion. We have now rewritten the relevant paragraphs to include answers to these and other comments. Regarding the discussion of the FLOPS these were never intended to be an accurate representation of the run-times but rather to provide an indication of how efficiently we are able to harness the GPU's resources. We have reworded the paragraph slightly to emphasize this.}
